---
title: "COVID-19 in Victoria"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
    theme: cosmo
    includes:
        in_header: goo_anal.htm
---

<style>                     
.value-box .icon .fa {
font-size: 180%;
color: rgba(255, 255, 255, 0.8);
top: 7px;
}
.value-box .value {
font-size: 23px;
margin: -5px 0 3px 0;
}
.value-box h6 {
font-size: 20px;
font-weight: bold;
margin-top: -8px;
}
.r0 {
margin-right: 72%;
}
.r1right {
margin-right: 43.4%;
}
h3 {
font-size:19px;
margin-right: 20px;
margin-top: 10.5px;
margin-bottom: 10.5px;
display: block;
font-weight: bold;
font-family: "Source Sans Pro",Calibri,Candara,Arial,sans-serif;
line-height: 1.1;
color: inherit;
}
.navbar{
  visibility: hidden
}
body {
    padding-top: 10px;
}
</style>

```{r include = FALSE}
# knitr::opts_chunk$set(echo=FALSE, message=FALSE,warning=FALSE)
# rmarkdown::render(input='covid_plots.Rmd', output_file = "index.html")
```

```{r message=FALSE, warning=FALSE}
# library(ggplot2)
library(tidyverse)
library(RCurl)
library(plotly)
library(RColorBrewer)
library(flexdashboard)
library(shiny)
library(zoo)
```

```{r}
source("covid_plots_functions.R")
```

<!-- ## initialize matrix with dates to calculate -->

```{r}
# # # initialize covid_data as of 27/04 and save it as covid_data.rda
# startdate <- as.Date("2020-03-23")
# enddate <- as.Date(Sys.Date())
# today <- unlist(str_split(tolower(gsub(" 0", " ",format(enddate, format="%B %d")))," "))
# #get end date
# if (get_dhhs_url(today[2],today[1])==FALSE){enddate <- enddate - 1}
# sel_dates <- seq(startdate, enddate, by="days")
# #fix for 16 april and 17 may
# sel_dates[sel_dates == "2020-04-16"] <- as.Date("2020-04-13")
# sel_dates[sel_dates == "2020-05-17"] <- as.Date("2020-04-16")
# days_to_plot <- tolower(gsub(" 0", " ",format(sel_dates, format="%B %d")))
# covid_data <- as.data.frame(do.call(rbind, str_split(days_to_plot," ")),stringsAsFactors =FALSE)
# covid_data <- cbind(covid_data,sel_dates)
# colnames(covid_data) <- c("month","day","date")
# covid_data$cases <- apply(covid_data,1,function(x) get_data_from_url(x['day'],x['month'],item="cases"))
# covid_data <- cbind(covid_data,setNames(data.frame(t(apply(covid_data,1,
#                              function(x) get_data_from_url(x['day'],x['month'],item="patients")))),
#                              c("hospital","icu","recovered")))
# covid_data$deaths <- apply(covid_data,1,function(x) get_data_from_url(x['day'],x['month'],item="deaths"))
# covid_data$community <- apply(covid_data,1,function(x) get_data_from_url(x['day'],x['month'],item="community"))
# covid_data <- fix_old_reports(covid_data)
# save(covid_data, file = "covid_data.rda")
# # covid_data
```

```{r}
get_today_data <- function(today.raw){
  today <- unlist(str_split(tolower(gsub(" 0", " ",format(today.raw, format="%B %d")))," "))
  if (get_dhhs_url(today[2],today[1])!=FALSE & !any(covid_data$date == today.raw)){
    update.covid <- setNames(data.frame(matrix(today,ncol=2)),c("month","day"))
    update.covid$date <- today.raw
    update.covid$cases <- get_data_from_url(update.covid$day, update.covid$month,item='cases')
    update.covid <- cbind(update.covid,setNames(data.frame(t(get_data_from_url(update.covid$day, update.covid$month,item='patients'))),c("hospital","icu","recovered")))
    update.covid$deaths <- get_data_from_url(update.covid$day, update.covid$month,item='deaths')
    update.covid$community <- get_data_from_url(update.covid$day, update.covid$month,item='community')
    return(update.covid)
  }
}

# if (get_dhhs_url(today[2],today[1])!=FALSE && !any(covid_data$date == today.raw)){
  #   update.covid <- setNames(data.frame(matrix(today,ncol=2)),c("month","day"))
  #   update.covid$date <- today.raw
  #   update.covid$cases <- get_data_from_url(update.covid$day, update.covid$month,item='cases')
  #   update.covid <- cbind(update.covid,setNames(data.frame(t(get_data_from_url(update.covid$day, update.covid$month,item='patients'))),c("hospital","icu","recovered")))
  #   update.covid$deaths <- get_data_from_url(update.covid$day, update.covid$month,item='deaths')
  #   update.covid$community <- get_data_from_url(update.covid$day, update.covid$month,item='community')
  #   covid_data <- rbind(covid_data,update.covid)
  # }
```


```{r}
# new process:
# load covid_data.rda
# check if today's link exists
# check if today has already been computed in covid_data
# run today and append it to covid_data
# save covid_data

load("covid_data.rda")
today.raw <- as.Date(Sys.Date())
today <- unlist(str_split(tolower(gsub(" 0", " ",format(today.raw, format="%B %d")))," "))
months <- 1:12
names(months) <- tolower(month.name)
today.weekday <- tolower(weekdays(as.Date(paste0(2020,"-",unname(months[today[1]]),"-",today[2]))))

# check if monday and then check if weekend was calculated
if (today.weekday == 'monday'){
  today.sat <- today.raw - 2
  update.covid <- get_today_data(today.sat)
  covid_data <- rbind(covid_data,update.covid)
  today.sun <- today.raw - 1
  update.covid <- get_today_data(today.sun)
  covid_data <- rbind(covid_data,update.covid)
} 

if (get_dhhs_url(today[2],today[1])!=FALSE & !any(covid_data$date == today.raw)){
  update.covid <- get_today_data(today.raw)
  covid_data <- rbind(covid_data,update.covid)
  save(covid_data, file = "covid_data.rda")
}
```

```{r}
covid_data <- covid_data %>%
  mutate(
    active = cases - recovered - deaths,
    recovered_perc = round(recovered / cases * 100,1),
    community_perc_total = round(community / cases * 100,1),
    cases_new = c(0,diff(cases)),
    community_new = c(0,diff(community)),
    community_perc_new = round(community_new / cases_new * 100,1),
  )
# covid_data
```

<!-- R0 approx -->

```{r}
# https://www.ub.edu/aqr/covid19/?p=349&lang=en#_ftn1
y <- covid_data$cases_new
t <- length(y)
k <- 14
q <- 14
# up <- sum(y[c((t-7):t)])
# down <- sum(y[c((t-7-7):(t-7))])
# ro <- round(up/down,2)
covid_data$ro <- NA
# get ro for all days
for (d in c((k+q):t)){
  up <- sum(y[c((d-q):d)])
  down <- sum(y[c((d-q-k):(d-k))])
  covid_data$ro[d] <- round(up/down,2)
}
```

```{r}
# mycols <- c("black", "firebrick","green","blue","orange","purple")
mycols <- c('black','#66C2A5','#FC8D62','#8DA0CB','#E78AC3','#A6D854','#FFD92F','#E5C494','#B3B3B3')
mycols <- c('black', brewer.pal(n = 8, name = 'Dark2'),'darkred')
mytext_x <- format(covid_data$date,format="%b")
mytext_x[duplicated(mytext_x)] <- ""
mytext_x <- paste(mytext_x,as.numeric(format(covid_data$date,format="%e")))
mytext_x <- str_replace(mytext_x,"^ ", "")
# remove all odd numbers in x axis for better readability
for (i in c(1:length(mytext_x))) {
  if (!is.na(as.numeric(mytext_x[i]))){
    if(as.numeric(mytext_x[i]) %% 2 == 0 | str_detect(mytext_x[i],"31")){
      mytext_x[i] <- " "
    } 
  }
  # if ((i %% 2 == 0 & !str_detect(mytext_x[i],"[a-z]")) | str_detect(mytext_x[i],"31")){
  #   mytext_x[i] <- " "}
}
covid_data$i <- as.numeric(rownames(covid_data))
fig <- plot_ly(data = covid_data,x = ~i)
fig <- fig %>% add_trace(y = ~cases, name = 'Cases',type='scatter', mode = 'lines',line = list(color = mycols[1]))
fig <- fig %>% add_trace(y = ~cases_new, name = 'Daily Cases', type = 'bar', yaxis = 'y2',marker = list(color = rgb(0,0,0,0.2)))
fig <- fig %>% add_trace(y = ~recovered, name = 'Recovered',type='scatter', mode = 'lines',line = list(color = mycols[2]))
fig <- fig %>% add_trace(y = ~active, name = 'Active',type='scatter', yaxis='y', mode = 'lines',line = list(color = mycols[3]))
fig <- fig %>% add_trace(y = ~community, name = 'Community',type='scatter', mode = 'lines',yaxis = 'y2',line = list(color = mycols[4]))
fig <- fig %>% add_trace(y = ~hospital, name = 'Hospital',type='scatter', mode = 'lines',yaxis = 'y2',line = list(color = mycols[5]))
fig <- fig %>% add_trace(y = ~icu, name = 'ICU',type='scatter', mode = 'lines',yaxis = 'y2',line = list(color = mycols[6]))
fig <- fig %>% add_trace(y = ~deaths, name = 'Deaths',type='scatter', mode = 'lines',yaxis = 'y2',line = list(color = mycols[7]))
fig <- fig %>% add_trace(y = ~ro, name = 'R0',type='scatter', mode = 'lines',yaxis = 'y3',line = list(color = mycols[10]))
my_ylim <- 25000
fig <- fig %>% layout(title = '',
                      xaxis = list(title = "Date",tickangle=-60,
                                   # type='date',
                                   # tickformat = '%b %e',
                                   # range = ~date,
                                   tickmode="array",
                                   tickvals=covid_data$i,
                                   ticktext=mytext_x,
                                   tickfont=list(size=10),
                                   autotick = F,
                                   domain = c(0,0.92),
                                   linewidth = 3,showgrid=T,
                                   linecolor='black',linewidth=0.5,mirror=T),
                      yaxis = list(side = 'left', title = 'Total / Recovered Cases (#)',
                                   linewidth = 3,
                                   range=c(0,my_ylim),
                                   linecolor='black',linewidth=0.5,mirror=T),
                      yaxis2 = list(side = 'right', overlaying = "y", anchor='x',
                                    title = 'Active & Daily Cases / Hospital / ICU \n Deaths / Community (# people)',
                                    linewidth = 3,
                                    showgrid=FALSE, zeroline=T, range=c(0,my_ylim/5), textangle = 90),
                      yaxis3 = list(side = 'right', overlaying = "y",
                                    tickfont=list(color=mycols[10]), titlefont=list(color=mycols[10]),
                                    title = 'R0', anchor='free', position=1, showline=TRUE,linecolor = mycols[10],
                                    linewidth = 3,
                                    showgrid=FALSE, zeroline=T, range=c(0,10), textangle = 90),
                      margin = list(r = 25),
                      legend = list(x = 0.01, y = 0.99, bordercolor = "black", borderwidth=0.5),
                      hovermode='x')
# fig
# https://plotly.com/r/axes/
# https://plotly.com/r/graphing-multiple-chart-types/
# https://plotly.com/r/reference/#layout-xaxis-tickmode
```

```{r}
# add 14 day average to covid_data
covid_data <- covid_data %>% mutate(avg14=round(rollmeanr(cases_new,14,fill=NA),0))
# add sum of community cases in the last 14 days (-16 to -2, as DHHS)
# to check
# for (i in c(1,2,3,4,5,6)){for (j in c(12:15)){d=length(com);print(c(i,j));print(com[d-i]-com[d-i-j])}}
covid_data$unk.total14 <- NA
for (day in c(17:length(covid_data$community))){
  covid_data$unk.total14[day] <- covid_data$community[day-1]-covid_data$community[day-16]}

fig2 <- plot_ly(data = covid_data,x = ~i)
fig2 <- fig2 %>% add_trace(y = ~cases_new, name = 'Daily Cases', type = 'bar', yaxis = 'y',marker = list(color = rgb(0,0,0,0.2)))
fig2 <- fig2 %>% add_trace(y = ~avg14, name = '14-day Avg', type='scatter', mode = 'lines',line = list(color = mycols[1]))
fig2 <- fig2 %>% add_segments(x=0,xend=max(covid_data$i),y=50,yend=50,name="Step 2 Threshold",showlegend=F)
fig2 <- fig2 %>% add_annotations(x= 150,y= 65,text = "Step 2 Threshold",showarrow = F,font = list(color = 'green', size = 10))
fig2 <- fig2 %>% add_segments(x=0,xend=max(covid_data$i),y=5,yend=5,name="Step 3 Threshold",showlegend=F)
fig2 <- fig2 %>% add_annotations(x= 150,y= 20,text = "Step 3 Threshold",showarrow = F,font = list(color = 'red', size = 10))
fig2 <- fig2 %>% add_trace(y = ~unk.total14, name = '14-day Unknown Total', type='scatter', mode = 'lines',line = list(color = mycols[3]))
my_ylim2 <- round(max(covid_data$cases_new)/1000+0.05,2)*1000
fig2 <- fig2 %>% layout(title = '',
                      xaxis = list(title = "Date",tickangle=-60,
                                   # type='date',
                                   # tickformat = '%b %e',
                                   # range = ~date,
                                   tickmode="array",
                                   tickvals=covid_data$i,
                                   ticktext=mytext_x,
                                   tickfont=list(size=10),
                                   autotick = F,
                                   domain = c(0,0.92),
                                   linewidth = 3,showgrid=F,
                                   linecolor='black',linewidth=0.5,mirror=T),
                      yaxis = list(side = 'left', title = 'Cases (#)',
                                   linewidth = 3,
                                   range=c(0,my_ylim2),
                                   linecolor='black',linewidth=0.5,mirror=T),
                      margin = list(r = 25),
                      # showlegend=FALSE,
                      legend = list(x = 0.01, y = 0.99, bordercolor = "black", borderwidth=0.5),
                      hovermode='x')
# fig2
```



<!-- ################ WEBSITE SETUP ############## -->
<!-- icons from https://fontawesome.com/icons?d=gallery&v=5.0.0&m=free -->

Row {data-height=80}
---------------------
```{r}
valueBox(
    value = tags$h2(paste0("COVID-19 in Victoria: ",format(Sys.Date(), format="%A, %B %e, %Y"))),
    color = ""
)
daily.status <- covid_data[dim(covid_data)[1],]
yesterday <- covid_data[dim(covid_data)[1]-1,]
maincolor <- 'gray'
updatecolor <- 'darkgray'
```

Row {data-height=100}
---------------------

### Total cases {.value-box}

```{r}
valueBox(
    value = daily.status$cases,
    icon = "fa-user",
    color = maincolor
  )
```

### Total deaths {.value-box}

```{r}
  valueBox(daily.status$deaths,
           icon = "fa-times-circle",
    color=maincolor
    )
```

### Recovered people {.value-box}

```{r}
valueBox(
    value = daily.status$recovered,
    icon = "fa-user-check",
    color=maincolor
)
```

### Active cases {.value-box}

```{r}
valueBox(
    value = daily.status$active,
    icon = "fa-user-clock",
    color=maincolor
)
```

### Patients in hospital {.value-box}

```{r}
valueBox(
    value = daily.status$hospital,
    icon = "fa-stethoscope",
    color=maincolor
)
```

### Patients in ICU {.value-box}

```{r}
valueBox(
    value = daily.status$icu,
    icon = "fa-ambulance",
    color=maincolor
)
```

### Community transmission {.value-box}

```{r}
valueBox(
    value = daily.status$community,
    icon = "fa-users",
    color=maincolor
)
```

Row {data-height=45}
---------------------

### Total cases {.value-box .no-mobile}

```{r}
v <- daily.status$cases_new
valueBox(
    value = "",
    caption = tags$h6(if (v >= 0) sprintf("%+d", v) else v),
    color = updatecolor
  )
```

### Total deaths {.value-box .no-mobile}

```{r}
v <- daily.status$deaths - yesterday$deaths
valueBox(
    value = "",
    caption = tags$h6(if (v >= 0) sprintf("%+d", v) else v),
    color = updatecolor
  )
```

### Recovered people {.value-box .no-mobile}

```{r}
v <- daily.status$recovered - yesterday$recovered
valueBox(
    value = "",
    caption = tags$h6(if (v >= 0) sprintf("%+d", v) else v),
    color = updatecolor
  )
```

### Active cases {.value-box .no-mobile}

```{r}
v <- daily.status$active - yesterday$active
valueBox(
    value = "",
    caption = tags$h6(if (v >= 0) sprintf("%+d", v) else v),
    color = updatecolor
  )
```

### Patients in hospital {.value-box .no-mobile}

```{r}
v <- daily.status$hospital - yesterday$hospital
valueBox(
    value = "",
    caption = tags$h6(if (v >= 0) sprintf("%+d", v) else v),
    color = updatecolor
  )
```

### Patients in ICU {.value-box .no-mobile}

```{r}
v <- daily.status$icu - yesterday$icu
valueBox(
    value = "",
    caption = tags$h6(if (v >= 0) sprintf("%+d", v) else v),
    color = updatecolor
  )
```

### Community transmission {.value-box .no-mobile}

```{r}
v <- daily.status$community - yesterday$community
valueBox(
    value = "",
    caption = tags$h6(if (v >= 0) sprintf("%+d", v) else v),
    color = updatecolor
  )
```

Row {data-height=50}
---------------------
```{r}
valueBox(
    value = tags$h3("Current R0"),
    color = ""
)
```

### {.value-box .no-mobile .r0}

```{r}
v <- daily.status$ro
valueBox(
    value = v,
    # caption = tags$h6(v),
    icon = "fa-exclamation-triangle",
    color = 'lightcoral'
)
```

Row {data-height=50}
---------------------
```{r}
valueBox(
    value = tags$h3("14d Status"),
    color = ""
)
```

### {.value-box .no-mobile}

```{r}
v <- daily.status$avg14
v <- paste("Average:   ",as.character(v))
valueBox(
    value = v,
    # caption = 'kk',
    icon = "fa-info-circle",
    color = 'cadetblue'
)
```

### {.value-box .no-mobile .r1right}

```{r}
v <- daily.status$unk.total14
v <- paste("Unknown Total:   ",as.character(v))
valueBox(
    value = v,
    # caption = 'kk',
    icon = "fa-sort-amount-down",
    color = 'darkcyan'
)
```

Row {data-height=5}
---------------------

Row {data-height=40}
---------------------

```{r}
valueBox(
    value = tags$h4("Weekly Changes"),
    color = ""
)
week.changes <- as.data.frame(t(as.numeric(daily.status[,-c(1,3)]) - as.numeric(covid_data[dim(covid_data)[1]-7,-c(1,3)])))
colnames(week.changes) <- colnames(daily.status)[-c(1,3)]
```

Row {data-height=50}
---------------------

### {.value-box .no-mobile}

```{r}
v = week.changes$cases
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 50) "fa-angle-double-up" else "fa-angle-up",
    color = if (v > 50) "firebrick" else "warning",
  )
```

### {.value-box .no-mobile}

```{r}
v = week.changes$deaths
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 5) "fa-angle-double-up" else if (v > 0) "fa-angle-up" else "fa-equals",
    color = if (v > 5) "firebrick" else if (v > 0) "warning" else "success"
  )
```

### {.value-box .no-mobile}

```{r}
v = week.changes$recovered
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 200) "fa-angle-double-up" else if (v > 0) "fa-angle-up" else "fa-equals",
    color = if (v >= 200) "success" else "primary"
  )
```

### {.value-box .no-mobile}

```{r}
v = week.changes$active
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 0) "fa-angle-up" else if (v < 0) "fa-angle-down" else "fa-equals",
    color = if (v <= 0) "success" else "warning"
  )
```

### {.value-box .no-mobile}

```{r}
v = week.changes$hospital
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 0) "fa-angle-up" else if (v < 0) "fa-angle-down" else "fa-equals",
    color = if (v <= 0) "success" else "warning"
  )
```

### {.value-box .no-mobile}

```{r}
v = week.changes$icu
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 0) "fa-angle-up" else if (v < 0) "fa-angle-down" else "fa-equals",
    color = if (v <= 0) "success" else "warning"
  )
```

### {.value-box .no-mobile}

```{r}
v = week.changes$community
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 0) "fa-angle-up" else if (v < 0) "fa-angle-down" else "fa-equals",
    color = if (v > 10) "firebrick" else if (v > 0) "warning" else "success"
  )
```


Row {data-height=40}
---------------------

```{r}
valueBox(
    value = tags$h4("Monthly Changes"),
    color = ""
)
month.changes <- as.data.frame(t(as.numeric(daily.status[,-c(1,3)]) - as.numeric(covid_data[dim(covid_data)[1]-30,-c(1,3)])))
colnames(month.changes) <- colnames(daily.status)[-c(1,3)]
```


Row {data-height=50}
---------------------

### {.value-box .no-mobile}

```{r}
v = month.changes$cases
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 50) "fa-angle-double-up" else "fa-angle-up",
    color = if (v > 50) "firebrick" else "warning"
  )
```

### {.value-box .no-mobile}

```{r}
v = month.changes$deaths
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 5) "fa-angle-double-up" else if (v > 0) "fa-angle-up" else "fa-equals",
    color = if (v > 5) "firebrick" else if (v > 0) "warning" else "success"
  )
```

### {.value-box .no-mobile}

```{r}
v = month.changes$recovered
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 200) "fa-angle-double-up" else "fa-angle-up",
    color = if (v >= 200) "success" else "primary"
  )
```

### {.value-box .no-mobile}

```{r}
v = month.changes$active
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 0) "fa-angle-up" else if (v < 0) "fa-angle-down" else "fa-equals",
    color = if (v <= 0) "success" else "warning"
  )
```

### {.value-box .no-mobile}

```{r}
v = month.changes$hospital
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 0) "fa-angle-up" else if (v < 0) "fa-angle-down" else "fa-equals",
    color = if (v <= 0) "success" else "warning"
  )
```

### {.value-box .no-mobile}

```{r}
v = month.changes$icu
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 0) "fa-angle-up" else if (v < 0) "fa-angle-down" else "fa-equals",
    color = if (v <= 0) "success" else "warning"
  )
```

### {.value-box .no-mobile}

```{r}
v = month.changes$community
valueBox(
    value = if (v >= 0) sprintf("%+d", v) else v,
    icon = if (v > 0) "fa-angle-up" else if (v < 0) "fa-angle-down" else "fa-equals",
    color = if (v > 10) "firebrick" else if (v > 0) "warning" else "success"
  )
```

Row {data-height=30}
---------------------

Row {data-height=500}
---------------------

###

```{r}
fig
```

Row {data-height=400}
---------------------

###

```{r}
fig2
```

Row {data-height=30}
---------------------
```{r}
update.date <- format(Sys.Date(), format="%A, %B %e at")
update.time <- format(Sys.time(), format="%H:%M")
update.text <- paste("Last updated on",update.date,update.time)
valueBox(
    value = tags$h5(update.text),
    color = ""
)
```

Row {data-height=20}
---------------------

##### Created by [\@RuizCSergio](http://twitter.com/RuizCSergio)
